### 2013-11-05 inst/examples/policycosts/plot_table.Rmd
update plot, smaller table
hide code

```{r}
opts_knit$set(upload.fun = socialR::flickr.url)
```

```{r}
require(ggplot2)
df <- read.csv("output.csv")
df <- df[2:8]

@@

```{r results="asis"}
print(xtable::xtable(df), type="html")
```

>>>>

```{r settings, include=FALSE}
opts_knit$set(upload.fun = socialR::flickr.url)
```

```{r fig.width=12, echo=FALSE}
require(ggplot2)
df <- read.csv("output.csv")
df <- df[2:8]

@@

```{r results="asis", echo=FALSE}
print(xtable::xtable(df), type="html")
```
